Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 1
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic (PV) systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space. Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load. Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying the equipment and deploying it in the field, as a safe approach to ensure the intended behavior. Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated to compare performance and soundness among automated verifiers. The experimental results reported by our automated verification method and by the simulation tools were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
\end{abstract}

@@

\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems. Instead, our novelty relies on an effective approach to perform validation of PV systems using formal methods, in a process that is intended to be done just after the system sizing, prior to buy equipment and deploy it at the field, as a way to ensure the intended behavior.}

\textcolor{red}{Here we compare model checking with simulation tool. However how they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then the model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking.}

>>>>

\begin{abstract}
\textcolor{red}{With declining costs and increasing performance, the deployment of renewable energy systems is growing faster. In $2017$, for the first time, the number of people without access to electricity dropped down below $1$ billion, but trends on energy access likewise fall short of global goals. Particular attention is given to stand-alone solar photovoltaic (PV) systems in rural areas or where grid extension is unfeasible. Tools to evaluate electrification projects are available, but they are based on simulations that do not cover all aspects of the design-space. Automated verification using model checking has proven to be an effective technique to validate complex (state transition) systems. This paper marks the first application of software model checking to formally verify the design of a stand-alone solar photovoltaic system, including solar panel, charge controller, battery, inverter, and electric load. Our main focus is on the solar PV project validation to be carried out just after the system sizing, i.e., prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior. Case studies, ranging from $253$ W to $814$ W, were used to evaluate this proposed approach and to compare that with specialized simulation tools. Different verification tools were evaluated to compare performance and soundness among automated verifiers. The experimental results reported by our automated verification method and by the simulation tools were compared with data collected from dwellers of the deployed cases, thereby showing the effectiveness of our approach, where specific conditions that lead to failures in a solar PV system are only detailed by the automated verification method.}
\end{abstract}

@@

\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems. Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.}

\textcolor{red}{Here we compare model checking with simulation tools. However how they work is completely different. On one hand, simulation depends on the choice of input variables (and their values) in order to obtain the output. On the other hand, model checking performs an exhaustive search with the goal of proving or violating a given property. In the latter case, if the property is violated (an unexpected behavior of the system), then the model checker presents the input that causes such a violation. Therefore, we can prove the absence of system flaws using model checking.}
